### 2022-05-02 src/text/3-applications-subsections/temporal-analysis.tex

The obtained flux points can be modelled using any of the available temporal and spectral models, or even using custom temporal models with spectroscopic variability. Alternatively, instead of  extracting a lightcurve, it is also possible to directly fit temporal models to the reduced datasets. By associating an appropriate SkyModel, consisting of both temporal and spectral components, to each dataset, a joint fitting across the datasets will directly return the best fit temporal and spectral parameters.

>>>>

The obtained flux points can be analytically modelled using the available, or user-implemented temporal models. Alternatively, instead of  extracting a lightcurve, it is also possible to directly fit temporal models to the reduced datasets. By associating an appropriate SkyModel, consisting of both temporal and spectral components, or using custom temporal models with spectroscopic variability, to each dataset, a joint fitting across the datasets will directly return the best fit temporal and spectral parameters.
